---
title: "Fish Handicap: if there is an interaction between mutational burden and tempearture shock?"
author: "Konstantin Popadin"
date: "7/July/2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls(all=TRUE))
library(knitr)
library(tidyverse)
library(kableExtra)
```

## Background
<br>
In experiments 1 and 2 main parameters (temperature, duration, ENU concentration) were tuned. 
Q - should we tune also the period of the exposition (eye stage - or before or after)?
<br>
Here, we analyze results of experiment number 3 performed in Dmitrovo
<br>
There are 4 families (two females and two males) there are 60 Petri dishes:
5 replications * 3 ENU (0,1,2) * 4 temperature conditions (38 degrees for 0, 30, 40 and 50 minutes; the base temperature is ~21)
<br>
For each of four families (female X male) several combinations of parameters were used: ENU (0,1,2) and temperature shocks (temperature and duration)
For each family five replications were used (5 Petri dishes) with 4 independent phenotypes, approximating fitness: (i) fertilized or not, (ii) hatched or not, (iii) swimming normally or not, (iv) swimming weirdly or not? 
Shock was applied on day 2-3 (eye stage) after fertilization and before hatching.
<br>
several fishes from 8 combinations (family x ENU) will be maintained in aquariums for one year to approximate fitness better. 
Q: is it ENU or shock? 
<br>
The key question: does decrease in fitness due to ENU interact with increase in fitness due to temperature?
<br><br><br>

#### 1. Read and describe data from the main (third) experiment 
***
```{r}
Fish = read.table('../data/fishes_shok.txt', header=TRUE)

head(Fish)
table(Fish$family)
table(Fish$temperature)
table(Fish$time)
summary(Fish$fertilization_per)
summary(Fish$hatched_per)
summary(Fish$swim_per)
```

PROBLEMS:
1. there is one Fish$swim_per == 240 which we need to delete
2. there is one where 

```{r}
Problem1 = Fish[Fish$swim_per > 100,]
Problem2 = Fish[Fish$swimming + Fish$freaks > Fish$hatched,]
Problem3 = Fish[Fish$hatched > Fish$alive,] # 0
Problem4 = Fish[Fish$alive > Fish$total,]   # 0

Problems = rbind(Problem1,Problem2)
Problems
dim(Fish)
Fish = Fish[!Fish$petri %in% Problems$petri,]
dim(Fish)
```

<br><br><br>

#### 2. turn the Petri-dish table to the individual level table, where each line is dedicated to one egg
***

```{r}
for (i in 1:nrow(Fish))
{ # i = 3
  OnePetriDish = Fish[i,]
  
  New = cbind(
    rep(OnePetriDish$petri,OnePetriDish$total),
    rep(OnePetriDish$family,OnePetriDish$total),
    rep(OnePetriDish$temperature,OnePetriDish$total),
    rep(OnePetriDish$time,OnePetriDish$total),
    rep(OnePetriDish$enu,OnePetriDish$total),
    c(rep(1,OnePetriDish$alive),rep(0,OnePetriDish$dead)),                                                       # FertilizedOrNot
    c(rep(1,OnePetriDish$hatched),rep(0,OnePetriDish$alive - OnePetriDish$hatched),rep(NA,OnePetriDish$dead)),   # HatchedOrNot
    c(rep(1,OnePetriDish$swimming + OnePetriDish$freaks),rep(0,OnePetriDish$hatched - OnePetriDish$swimming -  OnePetriDish$freaks),rep(NA,OnePetriDish$total-OnePetriDish$swimming-OnePetriDish$freaks - (OnePetriDish$hatched - OnePetriDish$swimming -  OnePetriDish$freaks))),                                                                                           # SwimmingOrNot      
    c(rep(1,OnePetriDish$swimming),rep(0,OnePetriDish$freaks),rep(NA,OnePetriDish$total-OnePetriDish$swimming-OnePetriDish$freaks)) 
                                                                                                                  # SwimmingNormallyOrNot
  )
  New = data.frame(New) 
  names(New)=c('petri','family','temperature','time','enu','FertilizedOrNot','HatchedOrNot','SwimmingOrNot','SwimmingNormallyOrNot') 
  
  if (i == 1) {Final = New}
  if (i >  1) {Final = rbind(Final,New)}
}
```

<br><br><br>

#### 3. derive two dummy variables: for mutants (DummyMutant1 and DummyMutant2) and three for shock (Final$DummyShock30, Final$DummyShock40, Final$DummyShock50) and InclusiveFitness and write down the table
***

```{r}
### derive InclusiveFitness as a total number of scores: Fertilized, Hatched and Swimming Normally
### fertilizedOrNot can't be a function of HeatShock!! it can be a function of only Mutagen. 
Temp = Final
Temp[is.na(Temp)]<-0 # substitute NA by zeroes
Temp$InclusiveFitness = as.numeric(Temp$FertilizedOrNot) + as.numeric(Temp$HatchedOrNot) + as.numeric(Temp$SwimmingNormallyOrNot) 
table(Temp$InclusiveFitness)
Final$InclusiveFitness1 = Temp$InclusiveFitness
Temp$InclusiveFitness = as.numeric(Temp$HatchedOrNot) + as.numeric(Temp$SwimmingNormallyOrNot) 
Final$InclusiveFitness2 = Temp$InclusiveFitness
  
### delete enu = 2 and keep only 0 (healthy) and 1 (mutants)
table(Final$enu)
Final$DummyMutant1 = NA
Final$DummyMutant2 = NA
table(Final$time)
Final$DummyShock30 = NA
Final$DummyShock40 = NA
Final$DummyShock50 = NA
for (i in 1:nrow(Final))
{ # i = 1
if (Final$enu[i] == 0) {Final$DummyMutant1[i] = 0}
if (Final$enu[i] == 1) {Final$DummyMutant1[i] = 1}  
if (Final$enu[i] == 0) {Final$DummyMutant2[i] = 0}
if (Final$enu[i] == 2) {Final$DummyMutant2[i] = 1}  

if (Final$time[i] == 0) {Final$DummyShock30[i] = 0}
if (Final$time[i] == 30) {Final$DummyShock30[i] = 1}
if (Final$time[i] == 0) {Final$DummyShock40[i] = 0}
if (Final$time[i] == 40) {Final$DummyShock40[i] = 1}
if (Final$time[i] == 0) {Final$DummyShock50[i] = 0}
if (Final$time[i] == 50) {Final$DummyShock50[i] = 1}

}

str(Final)
table(Final$DummyMutant1)
table(Final$DummyMutant2)
table(Final$DummyShock30)
table(Final$DummyShock40)
table(Final$DummyShock50)

Final$HatchedOrNot = as.numeric(Final$HatchedOrNot)
Final$SwimmingOrNot = as.numeric(Final$SwimmingOrNot)
Final$SwimmingNormallyOrNot = as.numeric(Final$SwimmingNormallyOrNot)
Final$FertilizedOrNot = as.numeric(Final$FertilizedOrNot)
Final$time = as.numeric(Final$time)

### derive HeatShockOrNot and HeatShockDuration
Final$HeatShockOrNot = as.numeric(Final$time)
table(Final$HeatShockOrNot)
Final[Final$HeatShockOrNot > 0,]$HeatShockOrNot = 1
table(Final$HeatShockOrNot)
Final$HeatShockDuration = as.numeric(Final$time)
table(Final$HeatShockDuration)

### derive MutagenOrNot and MutagenConcentration
table(Final$enu)
Final$MutagenOrNot = as.numeric(Final$enu)
Final[Final$MutagenOrNot == 2,]$MutagenOrNot = 1
table(Final$MutagenOrNot)
Final$MutagenConcentration = as.numeric(Final$enu)
Final[Final$MutagenConcentration == 1,]$MutagenConcentration = 1.5
table(Final$MutagenConcentration)

## families (female X male)
table(Final$family)
Final$Female1OrNot = as.numeric(gsub("x(.*)",'',Final$family));
Final[Final$Female1OrNot == 2,]$Female1OrNot = 0
table(Final$Female1OrNot)

Final$Male1OrNot = as.numeric(gsub("(.*)x",'',Final$family));
Final[Final$Male1OrNot == 2,]$Male1OrNot = 0
table(Final$Male1OrNot)
        
write.table(Final, '../data/Derive.txt', quote = FALSE, sep = '\t', row.names = FALSE)
```

<br><br><br>

#### 4. run generalized multiple model with InclusiveFitness as a function of several variables. Run familial analyses (2 out of three normal families show negative epist) 40 minuts, second male and second female.
***
```{r}
names(Final)
table(Final$InclusiveFitness1)
table(Final$InclusiveFitness2)
table(Final$HeatShockOrNot)
table(Final$HeatShockDuration)
table(Final$MutagenOrNot)
table(Final$MutagenConcentration)
table(Final$Female1OrNot)
table(Final$Male1OrNot)

summary(glm(Final$InclusiveFitness1 ~ Final$HeatShockDuration*Final$MutagenConcentration))
summary(glm(Final$InclusiveFitness1 ~ Final$HeatShockOrNot*Final$MutagenOrNot))
summary(glm(Final$HatchedOrNot ~ Final$HeatShockOrNot*Final$MutagenOrNot))
summary(glm(Final$InclusiveFitness2 ~ scale(Final$HeatShockDuration)*scale(Final$MutagenConcentration))) # the most correct model => positive epistasis 
summary(glm(Final$InclusiveFitness2 ~ scale(Final$HeatShockDuration)*scale(Final$MutagenConcentration)*Final$Female1OrNot + Final$Male1OrNot))
summary(glm(Final$InclusiveFitness2 ~ scale(Final$HeatShockOrNot)*scale(Final$MutagenOrNot)))

### at 40 minutes HatchedOrNot shows negative epistasis between temperature and mutagen
Final40 = Final[Final$HeatShockDuration!=30,]; Final40 = Final40[Final40$HeatShockDuration!=50,] 
summary(glm(Final40$InclusiveFitness2 ~ scale(Final40$HeatShockDuration)*scale(Final40$MutagenConcentration)))
summary(glm(Final40$HatchedOrNot ~ scale(Final40$HeatShockDuration)*scale(Final40$MutagenConcentration))) # !!!!
summary(glm(Final40$HatchedOrNot ~ scale(Final40$HeatShockOrNot)*scale(Final40$MutagenConcentration))) # !!!!
summary(glm(Final40$HatchedOrNot ~ scale(Final40$HeatShockOrNot)*scale(Final40$MutagenOrNot))) # !!!!
summary(glm(Final40$HatchedOrNot ~ scale(Final40$HeatShockOrNot)*scale(Final40$MutagenConcentration)+ Final40$Female1OrNot + Final40$Male1OrNot))

### female 1: no/weak interaction at all in case of hatched or not
Final1 = Final[Final$Female1OrNot==1,];
summary(glm(Final1$InclusiveFitness2 ~ scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration)))
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration))) # !!!!
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenConcentration))) # !!!!
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenOrNot))) # !!!!
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenConcentration)+ Final1$Male1OrNot))

### female 2: weak negative interaction
Final1 = Final[Final$Female1OrNot==0,];
summary(glm(Final1$InclusiveFitness2 ~ scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration)))
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration))) # !!!!
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenConcentration))) # !!!!
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenOrNot))) # !!!!
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenConcentration)+ Final1$Male1OrNot))

### male 1: strong positive
Final1 = Final[Final$Male1OrNot==1,];
summary(glm(Final1$InclusiveFitness2 ~ scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration)))
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration))) # !!!!
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenConcentration))) # !!!!
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenOrNot))) # !!!!
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenConcentration)+ Final1$Female1OrNot))

### male 2: negative for HatchedOrNot
Final1 = Final[Final$Male1OrNot==0,];
summary(glm(Final1$InclusiveFitness2 ~ scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration)))
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration))) # !!!!
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenConcentration))) # !!!!
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenOrNot))) # !!!!
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenConcentration)+ Final1$Female1OrNot))

#### THE BEST ANALYSES SHOULD BE DONE WITHIN EACH FAMILY: UNDER ALL ELSE EQUAL - THE SAME GENETICS OF MOTHER AND FATHER. out of four families one (1x1) has strange results (no effect of heat shock), another (2x1) no interaction and two others (2x2 and 1x2) negative interaction. So, not so bad! 

#### check whether each family shows expected simple trends: negative correlation with heat shock and negative with mutagen:

Final1 = Final[Final$family == '1x1',]; summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)+scale(Final1$MutagenConcentration))) # NO => which settings are wrong (which heat interval / mutagen)? check it later!!!
Final1 = Final[Final$family == '1x2',]; summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)+scale(Final1$MutagenConcentration))) # YES
Final1 = Final[Final$family == '2x1',]; summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)+scale(Final1$MutagenConcentration))) # YES
Final1 = Final[Final$family == '2x2',]; summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)+scale(Final1$MutagenConcentration))) # YES

Final1 = Final[Final$family != '1x1',]; summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)+scale(Final1$MutagenConcentration))) # NO =>

##### so, family 1x1 doesn't show expected trend - either something was wrong, or genetical combination is unusual (tolerability to stress)? we can exclude it from additional analyses because additional analyses are based on interaction of variables, but if there is no individual effect -> no sense to see the interaction. 

#### check whether each family shows interaction (different results but never positive significant)

Final1 = Final[Final$family == '1x2',]; summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration))) # NO
Final1 = Final[Final$family == '2x1',]; summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration))) # NO
Final1 = Final[Final$family == '2x2',]; summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration))) # YES

Final1 = Final[Final$family != '1x1',]; summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration))) # YES! THIS IS THE BEST AND REASONABLE RESULT TILL NOW

Final1 = Final[Final$family == '1x2',]; summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenOrNot))) # YES
Final1 = Final[Final$family == '2x1',]; summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenOrNot))) # NO
Final1 = Final[Final$family == '2x2',]; summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenOrNot))) # YES

Final1 = Final[Final$family != '1x1',]; summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenOrNot))) # NO

## family 1x1 HatchedOrNot positive, but effect of HeatShock is positive!
Final1 = Final[Final$family == '1x1',];
summary(glm(scale(Final1$InclusiveFitness1) ~ 0 +  scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration)))
summary(glm(scale(Final1$InclusiveFitness2) ~ 0 + scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration)))
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)+scale(Final1$MutagenConcentration))) # this model doesn't show effect of heat shock 
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration)))
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenConcentration)))
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenOrNot)))


## family 1x2 HatchedOrNot weakly negative
Final1 = Final[Final$family == '1x2',];
summary(glm(scale(Final1$InclusiveFitness1) ~ 0 +  scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration)))
summary(glm(scale(Final1$InclusiveFitness2) ~ 0 + scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration)))
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration)))
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenConcentration)))
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenOrNot)))

## family 2x1 HatchedOrNot no interaction
Final1 = Final[Final$family == '2x1',];
summary(glm(scale(Final1$InclusiveFitness1) ~ 0 +  scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration)))
summary(glm(scale(Final1$InclusiveFitness2) ~ 0 + scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration)))
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration)))
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenConcentration)))
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenOrNot)))

## family 2x2 HatchedOrNot == negative interaction
Final1 = Final[Final$family == '2x2',];
summary(glm(scale(Final1$InclusiveFitness1) ~ 0 +  scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration)))
summary(glm(scale(Final1$InclusiveFitness2) ~ 0 + scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration)))
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockDuration)*scale(Final1$MutagenConcentration)))
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenConcentration)))
summary(glm(Final1$HatchedOrNot ~ scale(Final1$HeatShockOrNot)*scale(Final1$MutagenOrNot)))

```

<br><br><br>

#### 5. run logistic regressions: Fitness ~ DummyMutant + DummyShock + DummyMutant*DummyShock
## Need to take into accnout families 
## interaction LikBez: https://www.youtube.com/watch?v=gjKzpxY4EqE
***
```{r}

# effect of a mutagen: AS EXPECTED FOR ALL FOUR PHENOTYPES !!!
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant1, family = binomial)) # -0.62380
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant2, family = binomial)) # -1.34791

summary(glm(Final$SwimmingOrNot ~ Final$DummyMutant1, family = binomial)) # -0.7701
summary(glm(Final$SwimmingOrNot ~ Final$DummyMutant2, family = binomial)) # -1.2542

summary(glm(Final$SwimmingNormallyOrNot ~ Final$DummyMutant1, family = binomial)) # -1.25509
summary(glm(Final$SwimmingNormallyOrNot ~ Final$DummyMutant2, family = binomial)) # -1.84769

summary(glm(Final$FertilizedOrNot ~ Final$DummyMutant1, family = binomial)) # -0.43879
summary(glm(Final$FertilizedOrNot ~ Final$DummyMutant2, family = binomial)) # -1.39644

# effect of a shock for Dummy Variables:  AS EXPECTED FOR HatchedOrNot and noisy for other phenotypes (including for FertilizedOrNot - where we don't expect to see any effects)
summary(glm(Final$HatchedOrNot ~ Final$DummyShock30, family = binomial)) # -0.39905
summary(glm(Final$HatchedOrNot ~ Final$DummyShock40, family = binomial)) # -1.22456
summary(glm(Final$HatchedOrNot ~ Final$DummyShock50, family = binomial)) # -1.21147

summary(glm(Final$SwimmingOrNot ~ Final$DummyShock30, family = binomial)) # -1.0765
summary(glm(Final$SwimmingOrNot ~ Final$DummyShock40, family = binomial)) # 0
summary(glm(Final$SwimmingOrNot ~ Final$DummyShock50, family = binomial)) # 0

summary(glm(Final$SwimmingNormallyOrNot ~ Final$DummyShock30, family = binomial)) # 0.62001
summary(glm(Final$SwimmingNormallyOrNot ~ Final$DummyShock40, family = binomial)) # 0
summary(glm(Final$SwimmingNormallyOrNot ~ Final$DummyShock50, family = binomial)) # 0.68270

summary(glm(Final$FertilizedOrNot ~ Final$DummyShock30, family = binomial)) # 0.20943
summary(glm(Final$FertilizedOrNot ~ Final$DummyShock40, family = binomial)) # -0.36805
summary(glm(Final$FertilizedOrNot ~ Final$DummyShock50, family = binomial)) # 0.24872

# effect of a shock as a continuous time variable

summary(Final$time)
summary(glm(Final$HatchedOrNot ~ Final$time, family = binomial)) # -0.025959
summary(glm(Final$SwimmingOrNot ~ Final$time, family = binomial)) # -0.006894
summary(glm(Final$SwimmingNormallyOrNot ~ Final$time, family = binomial)) # 0.011482 ?????

# additive effects of mutagen and shock:  AS EXPECTED!!!
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant1 + Final$DummyShock30, family = binomial)) # -0.61908 -0.54235
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant1 + Final$DummyShock40, family = binomial)) # -1.48739 -0.86483
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant1 + Final$DummyShock50, family = binomial)) # -0.56460 -1.40612
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant2 + Final$DummyShock30, family = binomial)) # -1.20038 -0.73067
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant2 + Final$DummyShock40, family = binomial)) # -2.4482  -1.5739
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant2 + Final$DummyShock50, family = binomial)) # -1.51755 -1.89158

summary(glm(Final$HatchedOrNot ~ scale(Final$DummyMutant1) + scale(Final$time), family = binomial)) # -0.34256 -0.51032 GOOD
summary(glm(Final$HatchedOrNot ~ scale(Final$DummyMutant2) + scale(Final$time), family = binomial)) # -0.85140 -0.70167 GOOD

summary(glm(Final$SwimmingOrNot ~ Final$DummyMutant1 + Final$DummyShock30, family = binomial))
summary(glm(Final$SwimmingOrNot ~ Final$DummyMutant1 + Final$DummyShock40, family = binomial))
summary(glm(Final$SwimmingOrNot ~ Final$DummyMutant1 + Final$DummyShock50, family = binomial))
summary(glm(Final$SwimmingOrNot ~ Final$DummyMutant2 + Final$DummyShock30, family = binomial)) # -0.8848 -1.1246
summary(glm(Final$SwimmingOrNot ~ Final$DummyMutant2 + Final$DummyShock40, family = binomial))
summary(glm(Final$SwimmingOrNot ~ Final$DummyMutant2 + Final$DummyShock50, family = binomial))

# epistatic effects of mutagen and shock:  UNCLEAR (negative under 40 minutes and positive otherwise...)

summary(glm(Final$HatchedOrNot ~ Final$DummyMutant1*Final$DummyShock30, family = binomial))   # 0.8869 ***
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant1*Final$DummyShock40, family = binomial))   # -0.6047 **
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant1*Final$DummyShock50, family = binomial))   # 1.0030 ***

summary(glm(Final$HatchedOrNot ~ Final$DummyMutant2*Final$DummyShock30, family = binomial))   # 0.5920 ***
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant2*Final$DummyShock40, family = binomial))   # -2.9985 ***
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant2*Final$DummyShock50, family = binomial))   # 0

summary(glm(Final$HatchedOrNot ~ scale(Final$DummyMutant1)*scale(Final$time), family = binomial)) # positive, fuck
summary(glm(Final$HatchedOrNot ~ scale(Final$DummyMutant2)*scale(Final$time), family = binomial)) # a bit negative, but non significant


# epistatic effects of mutagen and shock for each family separately - we need to add nested effect of families!   
Fam11=Final[Final$family == '1x1',]
Fam12=Final[Final$family == '1x2',]
Fam21=Final[Final$family == '2x1',]
Fam22=Final[Final$family == '2x2',]

## Fam11 
summary(glm(Fam11$HatchedOrNot ~ Fam11$DummyMutant1*Fam11$DummyShock30)) # +
summary(glm(Fam11$HatchedOrNot ~ Fam11$DummyMutant1*Fam11$DummyShock40))
summary(glm(Fam11$HatchedOrNot ~ Fam11$DummyMutant1*Fam11$DummyShock50)) # + 
summary(glm(Fam11$HatchedOrNot ~ Fam11$DummyMutant2*Fam11$DummyShock30))
summary(glm(Fam11$HatchedOrNot ~ Fam11$DummyMutant2*Fam11$DummyShock40))
summary(glm(Fam11$HatchedOrNot ~ Fam11$DummyMutant2*Fam11$DummyShock50)) # +

## Fam12
summary(glm(Fam12$HatchedOrNot ~ Fam12$DummyMutant1*Fam12$DummyShock30))
summary(glm(Fam12$HatchedOrNot ~ Fam12$DummyMutant1*Fam12$DummyShock40))
summary(glm(Fam12$HatchedOrNot ~ Fam12$DummyMutant1*Fam12$DummyShock50)) # + 
summary(glm(Fam12$HatchedOrNot ~ Fam12$DummyMutant2*Fam12$DummyShock30))
summary(glm(Fam12$HatchedOrNot ~ Fam12$DummyMutant2*Fam12$DummyShock40))
summary(glm(Fam12$HatchedOrNot ~ Fam12$DummyMutant2*Fam12$DummyShock50)) # +

## Fam21 
summary(glm(Fam21$HatchedOrNot ~ Fam21$DummyMutant1*Fam21$DummyShock30))
summary(glm(Fam21$HatchedOrNot ~ Fam21$DummyMutant1*Fam21$DummyShock40))
summary(glm(Fam21$HatchedOrNot ~ Fam21$DummyMutant1*Fam21$DummyShock50)) # - 
summary(glm(Fam21$HatchedOrNot ~ Fam21$DummyMutant2*Fam21$DummyShock30)) # +
summary(glm(Fam21$HatchedOrNot ~ Fam21$DummyMutant2*Fam21$DummyShock40))
summary(glm(Fam21$HatchedOrNot ~ Fam21$DummyMutant2*Fam21$DummyShock50)) 

## Fam22 
summary(glm(Fam22$HatchedOrNot ~ Fam22$DummyMutant1*Fam22$DummyShock30))
summary(glm(Fam22$HatchedOrNot ~ Fam22$DummyMutant1*Fam22$DummyShock40))
summary(glm(Fam22$HatchedOrNot ~ Fam22$DummyMutant1*Fam22$DummyShock50)) 
summary(glm(Fam22$HatchedOrNot ~ Fam22$DummyMutant2*Fam22$DummyShock30)) 
summary(glm(Fam22$HatchedOrNot ~ Fam22$DummyMutant2*Fam22$DummyShock40)) # -
summary(glm(Fam22$HatchedOrNot ~ Fam22$DummyMutant2*Fam22$DummyShock50)) # - 

```

<br><br><br>

#### 5. the best summary - cherry picking (HatchedOrNot)
***
```{r}

summary(glm(Final$HatchedOrNot ~ Final$DummyMutant1*Final$DummyShock40, family = binomial))   # -0.6047 **

summary(glm(Final$HatchedOrNot ~ Final$DummyMutant2*Final$DummyShock40, family = binomial))   # -2.9985 ***

summary(glm(Final$HatchedOrNot ~ scale(Final$DummyMutant2)*scale(Final$time), family = binomial)) # a bit negative, but non significant

summary(glm(Fam22$HatchedOrNot ~ Fam22$DummyMutant1*Fam22$DummyShock40)) # -
summary(glm(Fam22$HatchedOrNot ~ Fam22$DummyMutant1*Fam22$DummyShock50)) # -
summary(glm(Fam22$HatchedOrNot ~ Fam22$DummyMutant2*Fam22$DummyShock40)) # -
summary(glm(Fam22$HatchedOrNot ~ Fam22$DummyMutant2*Fam22$DummyShock50)) # - 

```