---
title: "Fish Handicap: if there is an interaction between mutational burden and tempearture shock?"
author: "Konstantin Popadin"
date: "7/July/2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls(all=TRUE))
library(knitr)
library(tidyverse)
library(kableExtra)
```

## Background
<br>
In experiments 1 and 2 main parameters (temperature, duration, ENU concentration) were tuned. 
Q - should we tune also the period of the exposition (eye stage - or before or after)?
<br>
Here, we analyze results of experiment number 3 performed in Dmitrovo
<br>
There are 4 families (two females and two males) there are 60 Petri dishes:
5 replications * 3 ENU (0,1,2) * 4 temperature conditions (38 degrees for 0, 30, 40 and 50 minutes; the base temperature is ~21)
<br>
For each of four families (female X male) sefveral combinations of parameters were used: ENU (0,1,2) and temperature shocks (temperature and duration)
For each family five replications were used (5 Petri dishes) with 4 independent phenotypes, approximating fitness: (i) fertilized or not, (ii) hatched or not, (iii) swimming normally or not, (iv) swimming weirdly or not? 
Shock was applied on day 2-3 (eye stage) after fertilization and before hatching.
<br>
several fishes from 8 combinations (family x ENU) will be maintained in aquariums for one year to approximate fitness better. 
Q: is it ENU or shock? 
<br>
The key question: does decrease in fitness due to ENU interact with increase in fitness due to temperature?
<br><br><br>

#### 1. Read and describe data from the main (third) experiment 
***
```{r}
Fish = read.table('../data/fishes_shok.txt', header=TRUE)

head(Fish)
table(Fish$family)
table(Fish$temperature)
table(Fish$time)
summary(Fish$fertilization_per)
summary(Fish$hatched_per)
summary(Fish$swim_per)
```

PROBLEMS:
1. there is one Fish$swim_per == 240 which we need to delete
2. there is one where 

```{r}
Problem1 = Fish[Fish$swim_per > 100,]
Problem2 = Fish[Fish$swimming + Fish$freaks > Fish$hatched,]
Problem3 = Fish[Fish$hatched > Fish$alive,] # 0
Problem4 = Fish[Fish$alive > Fish$total,]   # 0

Problems = rbind(Problem1,Problem2)
Problems
dim(Fish)
Fish = Fish[!Fish$petri %in% Problems$petri,]
dim(Fish)
```

<br><br><br>

#### 2. turn the Petri-dish table to the individual level table, where each line is dedicated to one egg
***

```{r}
for (i in 1:nrow(Fish))
{ # i = 3
  OnePetriDish = Fish[i,]
  
  New = cbind(
    rep(OnePetriDish$petri,OnePetriDish$total),
    rep(OnePetriDish$family,OnePetriDish$total),
    rep(OnePetriDish$temperature,OnePetriDish$total),
    rep(OnePetriDish$time,OnePetriDish$total),
    rep(OnePetriDish$enu,OnePetriDish$total),
    c(rep(1,OnePetriDish$alive),rep(0,OnePetriDish$dead)),                                                       # FertilizedOrNot
    c(rep(1,OnePetriDish$hatched),rep(0,OnePetriDish$alive - OnePetriDish$hatched),rep(NA,OnePetriDish$dead)),   # HatchedOrNot
    c(rep(1,OnePetriDish$swimming + OnePetriDish$freaks),rep(0,OnePetriDish$hatched - OnePetriDish$swimming -  OnePetriDish$freaks),rep(NA,OnePetriDish$total-OnePetriDish$swimming-OnePetriDish$freaks - (OnePetriDish$hatched - OnePetriDish$swimming -  OnePetriDish$freaks))),                                                                                           # SwimmingOrNot      
    c(rep(1,OnePetriDish$swimming),rep(0,OnePetriDish$freaks),rep(NA,OnePetriDish$total-OnePetriDish$swimming-OnePetriDish$freaks)) 
                                                                                                                  # SwimmingNormallyOrNot
  )
  New = data.frame(New) 
  names(New)=c('petri','family','temperature','time','enu','FertilizedOrNot','HatchedOrNot','SwimmingOrNot','SwimmingNormallyOrNot') 
  
  if (i == 1) {Final = New}
  if (i >  1) {Final = rbind(Final,New)}
}
```

<br><br><br>

#### 3. derive two dummy variables for mutants (DummyMutant1 and DummyMutant2) and three for shock (Final$DummyShock30, Final$DummyShock40, Final$DummyShock50)
***

```{r}
### delete enu = 2 and keep only 0 (healthy) and 1 (mutants)
table(Final$enu)
Final$DummyMutant1 = NA
Final$DummyMutant2 = NA
table(Final$time)
Final$DummyShock30 = NA
Final$DummyShock40 = NA
Final$DummyShock50 = NA
for (i in 1:nrow(Final))
{ # i = 1
if (Final$enu[i] == 0) {Final$DummyMutant1[i] = 0}
if (Final$enu[i] == 1) {Final$DummyMutant1[i] = 1}  
if (Final$enu[i] == 0) {Final$DummyMutant2[i] = 0}
if (Final$enu[i] == 2) {Final$DummyMutant2[i] = 1}  

if (Final$time[i] == 0) {Final$DummyShock30[i] = 0}
if (Final$time[i] == 30) {Final$DummyShock30[i] = 1}
if (Final$time[i] == 0) {Final$DummyShock40[i] = 0}
if (Final$time[i] == 40) {Final$DummyShock40[i] = 1}
if (Final$time[i] == 0) {Final$DummyShock50[i] = 0}
if (Final$time[i] == 50) {Final$DummyShock50[i] = 1}

}

str(Final)
table(Final$DummyMutant1)
table(Final$DummyMutant2)
table(Final$DummyShock30)
table(Final$DummyShock40)
table(Final$DummyShock50)

Final$HatchedOrNot = as.numeric(Final$HatchedOrNot)
Final$SwimmingOrNot = as.numeric(Final$SwimmingOrNot)
Final$SwimmingNormallyOrNot = as.numeric(Final$SwimmingNormallyOrNot)
Final$FertilizedOrNot = as.numeric(Final$FertilizedOrNot)
Final$time = as.numeric(Final$time)
```

<br><br><br>

#### 4. run logistic regressions: Fitness ~ DummyMutant + DummyShock + DummyMutant*DummyShock
## Need to take into accnout families 
## interaction LikBez: https://www.youtube.com/watch?v=gjKzpxY4EqE
***
```{r}

# effect of a mutagen: AS EXPECTED FOR ALL FOUR PHENOTYPES !!!
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant1, family = binomial)) # -0.62380
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant2, family = binomial)) # -1.34791

summary(glm(Final$SwimmingOrNot ~ Final$DummyMutant1, family = binomial)) # -0.7701
summary(glm(Final$SwimmingOrNot ~ Final$DummyMutant2, family = binomial)) # -1.2542

summary(glm(Final$SwimmingNormallyOrNot ~ Final$DummyMutant1, family = binomial)) # -1.25509
summary(glm(Final$SwimmingNormallyOrNot ~ Final$DummyMutant2, family = binomial)) # -1.84769

summary(glm(Final$FertilizedOrNot ~ Final$DummyMutant1, family = binomial)) # -0.43879
summary(glm(Final$FertilizedOrNot ~ Final$DummyMutant2, family = binomial)) # -1.39644

# effect of a shock for Dummy Variables:  AS EXPECTED FOR HatchedOrNot and noisy for other phenotypes (including for FertilizedOrNot - where we don't expect to see any effects)
summary(glm(Final$HatchedOrNot ~ Final$DummyShock30, family = binomial)) # -0.39905
summary(glm(Final$HatchedOrNot ~ Final$DummyShock40, family = binomial)) # -1.22456
summary(glm(Final$HatchedOrNot ~ Final$DummyShock50, family = binomial)) # -1.21147

summary(glm(Final$SwimmingOrNot ~ Final$DummyShock30, family = binomial)) # -1.0765
summary(glm(Final$SwimmingOrNot ~ Final$DummyShock40, family = binomial)) # 0
summary(glm(Final$SwimmingOrNot ~ Final$DummyShock50, family = binomial)) # 0

summary(glm(Final$SwimmingNormallyOrNot ~ Final$DummyShock30, family = binomial)) # 0.62001
summary(glm(Final$SwimmingNormallyOrNot ~ Final$DummyShock40, family = binomial)) # 0
summary(glm(Final$SwimmingNormallyOrNot ~ Final$DummyShock50, family = binomial)) # 0.68270

summary(glm(Final$FertilizedOrNot ~ Final$DummyShock30, family = binomial)) # 0.20943
summary(glm(Final$FertilizedOrNot ~ Final$DummyShock40, family = binomial)) # -0.36805
summary(glm(Final$FertilizedOrNot ~ Final$DummyShock50, family = binomial)) # 0.24872

# effect of a shock as a continuous time variable

summary(Final$time)
summary(glm(Final$HatchedOrNot ~ Final$time, family = binomial)) # -0.025959
summary(glm(Final$SwimmingOrNot ~ Final$time, family = binomial)) # -0.006894
summary(glm(Final$SwimmingNormallyOrNot ~ Final$time, family = binomial)) # 0.011482 ?????

# additive effects of mutagen and shock:  AS EXPECTED!!!
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant1 + Final$DummyShock30, family = binomial)) # -0.61908 -0.54235
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant1 + Final$DummyShock40, family = binomial)) # -1.48739 -0.86483
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant1 + Final$DummyShock50, family = binomial)) # -0.56460 -1.40612
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant2 + Final$DummyShock30, family = binomial)) # -1.20038 -0.73067
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant2 + Final$DummyShock40, family = binomial)) # -2.4482  -1.5739
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant2 + Final$DummyShock50, family = binomial)) # -1.51755 -1.89158

summary(glm(Final$HatchedOrNot ~ scale(Final$DummyMutant1) + scale(Final$time), family = binomial)) # -0.34256 -0.51032 GOOD
summary(glm(Final$HatchedOrNot ~ scale(Final$DummyMutant2) + scale(Final$time), family = binomial)) # -0.85140 -0.70167 GOOD

summary(glm(Final$SwimmingOrNot ~ Final$DummyMutant1 + Final$DummyShock30, family = binomial))
summary(glm(Final$SwimmingOrNot ~ Final$DummyMutant1 + Final$DummyShock40, family = binomial))
summary(glm(Final$SwimmingOrNot ~ Final$DummyMutant1 + Final$DummyShock50, family = binomial))
summary(glm(Final$SwimmingOrNot ~ Final$DummyMutant2 + Final$DummyShock30, family = binomial)) # -0.8848 -1.1246
summary(glm(Final$SwimmingOrNot ~ Final$DummyMutant2 + Final$DummyShock40, family = binomial))
summary(glm(Final$SwimmingOrNot ~ Final$DummyMutant2 + Final$DummyShock50, family = binomial))

# epistatic effects of mutagen and shock:  UNCLEAR (negative under 40 minutes and positive otherwise...)
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant1*Final$DummyShock30, family = binomial))   # 0.8869 ***
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant1*Final$DummyShock40, family = binomial))   # -0.6047 **
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant1*Final$DummyShock50, family = binomial))   # 1.0030 ***

summary(glm(Final$HatchedOrNot ~ Final$DummyMutant2*Final$DummyShock30, family = binomial))   # 0.5920 ***
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant2*Final$DummyShock40, family = binomial))   # -2.9985 ***
summary(glm(Final$HatchedOrNot ~ Final$DummyMutant2*Final$DummyShock50, family = binomial))   # 0

summary(glm(Final$HatchedOrNot ~ scale(Final$DummyMutant1)*scale(Final$time), family = binomial)) # positive, fuck
summary(glm(Final$HatchedOrNot ~ scale(Final$DummyMutant2)*scale(Final$time), family = binomial)) # a bit negative, but non significant



# epistatic effects of mutagen and shock for each family separately - we need to add nested effect of families!   
Fam11=Final[Final$family == '1x1',]
Fam12=Final[Final$family == '1x2',]
Fam21=Final[Final$family == '2x1',]
Fam22=Final[Final$family == '2x2',]

## Fam11 
summary(glm(Fam11$HatchedOrNot ~ Fam11$DummyMutant1*Fam11$DummyShock30)) # +
summary(glm(Fam11$HatchedOrNot ~ Fam11$DummyMutant1*Fam11$DummyShock40))
summary(glm(Fam11$HatchedOrNot ~ Fam11$DummyMutant1*Fam11$DummyShock50)) # + 
summary(glm(Fam11$HatchedOrNot ~ Fam11$DummyMutant2*Fam11$DummyShock30))
summary(glm(Fam11$HatchedOrNot ~ Fam11$DummyMutant2*Fam11$DummyShock40))
summary(glm(Fam11$HatchedOrNot ~ Fam11$DummyMutant2*Fam11$DummyShock50)) # +

## Fam12
summary(glm(Fam12$HatchedOrNot ~ Fam12$DummyMutant1*Fam12$DummyShock30))
summary(glm(Fam12$HatchedOrNot ~ Fam12$DummyMutant1*Fam12$DummyShock40))
summary(glm(Fam12$HatchedOrNot ~ Fam12$DummyMutant1*Fam12$DummyShock50)) # + 
summary(glm(Fam12$HatchedOrNot ~ Fam12$DummyMutant2*Fam12$DummyShock30))
summary(glm(Fam12$HatchedOrNot ~ Fam12$DummyMutant2*Fam12$DummyShock40))
summary(glm(Fam12$HatchedOrNot ~ Fam12$DummyMutant2*Fam12$DummyShock50)) # +

## Fam21 
summary(glm(Fam21$HatchedOrNot ~ Fam21$DummyMutant1*Fam21$DummyShock30))
summary(glm(Fam21$HatchedOrNot ~ Fam21$DummyMutant1*Fam21$DummyShock40))
summary(glm(Fam21$HatchedOrNot ~ Fam21$DummyMutant1*Fam21$DummyShock50)) # - 
summary(glm(Fam21$HatchedOrNot ~ Fam21$DummyMutant2*Fam21$DummyShock30)) # +
summary(glm(Fam21$HatchedOrNot ~ Fam21$DummyMutant2*Fam21$DummyShock40))
summary(glm(Fam21$HatchedOrNot ~ Fam21$DummyMutant2*Fam21$DummyShock50)) 

## Fam22 
summary(glm(Fam22$HatchedOrNot ~ Fam22$DummyMutant1*Fam22$DummyShock30))
summary(glm(Fam22$HatchedOrNot ~ Fam22$DummyMutant1*Fam22$DummyShock40))
summary(glm(Fam22$HatchedOrNot ~ Fam22$DummyMutant1*Fam22$DummyShock50)) 
summary(glm(Fam22$HatchedOrNot ~ Fam22$DummyMutant2*Fam22$DummyShock30)) 
summary(glm(Fam22$HatchedOrNot ~ Fam22$DummyMutant2*Fam22$DummyShock40)) # -
summary(glm(Fam22$HatchedOrNot ~ Fam22$DummyMutant2*Fam22$DummyShock50)) # - 

```


