---
title: "Fishашыр Handicap: if there is an interaction between mutational burden and tempearture shock?"
author: "Konstantin Popadin"
date: "7/July/2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls(all=TRUE))
library(knitr)
library(tidyverse)
library(kableExtra)
```

## Background
<br>
In experiments 1 and 2 main parameters (temperature, duration, ENU concentration) were tuned. 
Q - should we tune also the period of the exposition (eye stage - or before or after)?
<br>
Here, we analyze results of experiment number 3 performed in Dmitrovo
<br>
There are 4 families (two females and two males) there are 60 Petri dishes:
5 replications * 3 ENU (0,1,2) * 4 temperature conditions (38 degrees for 0, 30, 40 and 50 minutes; the base temperature is ~21)
<br>
For each of four families (female X male) sefveral combinations of parameters were used: ENU (0,1,2) and temperature shocks (temperature and duration)
For each family five replications were used (5 Petri dishes) with 4 independent phenotypes, approximating fitness: (i) fertilized or not, (ii) hatched or not, (iii) swimming normally or not, (iv) swimming weirdly or not? 
Shock was applied on day 2-3 (eye stage) after fertilization and before hatching.
<br>
several fishes from 8 combinations (family x ENU) will be maintained in aquariums for one year to approximate fitness better. 
Q: is it ENU or shock? 
<br>
The key question: does decrease in fitness due to ENU interact with increase in fitness due to temperature?
<br><br><br>

#### 1. Read and describe data from the main (third) experiment 
***
```{r}
Fish = read.table('C:/fish/fishes_shok.txt', header=TRUE)

head(Fish)
table(Fish$family)
table(Fish$temperature)
table(Fish$time)
summary(Fish$fertilization_per)
summary(Fish$hatched_per)
summary(Fish$swim_per)
```

PROBLEMS:
1. there is one Fish$swim_per == 240 which we need to delete
2. there is one where 

```{r}
Problem1 = Fish[Fish$swim_per > 100,]
Problem2 = Fish[Fish$swimming + Fish$freaks > Fish$hatched,]
Problem3 = Fish[Fish$hatched > Fish$alive,] # 0
Problem4 = Fish[Fish$alive > Fish$total,]   # 0

Problems = rbind(Problem1,Problem2)
Problems
dim(Fish)
Fish = Fish[!Fish$petri %in% Problems$petri,]
dim(Fish)
```

<br><br><br>

#### 2. turn the Petri-dish table to the individual level table, where each line is dedicated to one egg
***

```{r}
for (i in 1:nrow(Fish))
{ # i = 3
  OnePetriDish = Fish[i,]
  
  New = cbind(
    rep(OnePetriDish$petri,OnePetriDish$total),
    rep(OnePetriDish$family,OnePetriDish$total),
    rep(OnePetriDish$temperature,OnePetriDish$total),
    rep(OnePetriDish$time,OnePetriDish$total),
    rep(OnePetriDish$enu,OnePetriDish$total),
    c(rep(1,OnePetriDish$alive),rep(0,OnePetriDish$dead)),                                                       # FertilizedOrNot
    c(rep(1,OnePetriDish$hatched),rep(0,OnePetriDish$alive - OnePetriDish$hatched),rep(NA,OnePetriDish$dead)),   # HatchedOrNot
    c(rep(1,OnePetriDish$swimming + OnePetriDish$freaks),rep(0,OnePetriDish$hatched - OnePetriDish$swimming -  OnePetriDish$freaks),rep(NA,OnePetriDish$total-OnePetriDish$swimming-OnePetriDish$freaks - (OnePetriDish$hatched - OnePetriDish$swimming -  OnePetriDish$freaks))),                                                                                           # SwimmingOrNot      
    c(rep(1,OnePetriDish$swimming),rep(0,OnePetriDish$freaks),rep(NA,OnePetriDish$total-OnePetriDish$swimming-OnePetriDish$freaks)) 
                                                                                                                  # SwimmingNormallyOrNot
  )
  New = data.frame(New) 
  names(New)=c('petri','family','temperature','time','enu','FertilizedOrNot','HatchedOrNot','SwimmingOrNot','SwimmingNormallyOrNot') 
  
  if (i == 1) {Final = New}
  if (i >  1) {Final = rbind(Final,New)}
}
```

<br><br><br>

#### 3. derive two dummy variables for mutants (DummyMutant1 and DummyMutant2) and three for shock (Final$DummyShock30, Final$DummyShock40, Final$DummyShock50)
***

```{r}
### delete enu = 2 and keep only 0 (healthy) and 1 (mutants)
table(Final$enu)
Final$DummyMutant1 = NA
Final$DummyMutant2 = NA
table(Final$time)
Final$DummyShock30 = NA
Final$DummyShock40 = NA
Final$DummyShock50 = NA
for (i in 1:nrow(Final))
{ # i = 1
if (Final$enu[i] == 0) {Final$DummyMutant1[i] = 0}
if (Final$enu[i] == 1) {Final$DummyMutant1[i] = 1}  
if (Final$enu[i] == 0) {Final$DummyMutant2[i] = 0}
if (Final$enu[i] == 2) {Final$DummyMutant2[i] = 1}  

if (Final$time[i] == 0) {Final$DummyShock30[i] = 0}
if (Final$time[i] == 30) {Final$DummyShock30[i] = 1}
if (Final$time[i] == 0) {Final$DummyShock40[i] = 0}
if (Final$time[i] == 40) {Final$DummyShock40[i] = 1}
if (Final$time[i] == 0) {Final$DummyShock50[i] = 0}
if (Final$time[i] == 50) {Final$DummyShock50[i] = 1}

}

str(Final)
table(Final$DummyMutant1)
table(Final$DummyMutant2)
table(Final$DummyShock30)
table(Final$DummyShock40)
table(Final$DummyShock50)

Final$HatchedOrNot = as.numeric(Final$HatchedOrNot)
Final$SwimmingOrNot = as.numeric(Final$SwimmingOrNot)
Final$SwimmingNormallyOrNot = as.numeric(Final$SwimmingNormallyOrNot)
Final$FertilizedOrNot = as.numeric(Final$FertilizedOrNot)
Final$time = as.numeric(Final$time)
```

<br><br><br>




#STarting PDF
pdf(file='ENU0111.pdf')
#Step sep our concentrations by 0 1 2
Fish$enu = as.factor(Fish$enu)
enu_n_0 = paste('N=',nrow(Fish[Fish$enu == 0,]),sep='')
enu_n_1 = paste('N=',nrow(Fish[Fish$enu == 1,]),sep='')
enu_n_2 = paste('N=',nrow(Fish[Fish$enu == 2,]),sep='')
#sasha







getwd()

#Step sep our concentrations by 0 1 2
Fish$enu = as.factor(Fish$enu)
enu_n_0 = paste('N=',nrow(Fish[Fish$enu == 0,]),sep='')
enu_n_1 = paste('N=',nrow(Fish[Fish$enu == 1,]),sep='')
enu_n_2 = paste('N=',nrow(Fish[Fish$enu == 2,]),sep='')

#fertilization_per

boxplot(Fish[Fish$enu==0,]$fertilization_per, Fish[Fish$enu==1,]$fertilization_per, Fish[Fish$enu==2,]$fertilization_per, notch=TRUE, scale_x_discrete(labels=c(paste("0", enu_n_0,sep='\n'), paste("1", enu_n_1,sep='\n'), paste("2", enu_n_2,sep='\n')))


scale_x_discrete(labels=c(paste("0", enu_n_0,sep='\n'), paste("1", enu_n_1,sep='\n'), paste("2", enu_n_2,sep='\n')))

#hatched_per
paste("0", number_of_zero), ()
boxplot(Fish[Fish$enu==0,]$hatched_per, Fish[Fish$enu==1,]$hatched_per, Fish[Fish$enu==2,]$hatched_per, notch=TRUE, names = c(paste("0, N=", number_of_zero), '1', '2'), xlab = "enu", ylab = "hatched_per")

wilcox.test(Fish[Fish$enu==0,]$swim_per, Fish[Fish$enu==1,]$swim_per)
#swim_per
paste("0", enu_n_0)
paste("1", enu_n_1)
paste("2", enu_n_2)


boxplot(Fish[Fish$enu==0,]$swim_per, Fish[Fish$enu==1,]$swim_per, Fish[Fish$enu==2,]$swim_per, notch=TRUE, names = c(paste("0,", enu_n_0,sep='\n'), paste("1,", enu_n_1,sep='\n'), paste("2,", enu_n_2,sep='\n')), xlab = "enu", ylab = "swim_per")

wilcox.test(Fish[Fish$enu==0,]$swim_per, Fish[Fish$enu==1,]$swim_per)

#freaks_per
paste("0", number_of_zero)
boxplot(Fish[Fish$enu==0,]$freaks_per, Fish[Fish$enu==1,]$freaks_per, Fish[Fish$enu==2,]$freaks_per, notch=TRUE, names = c((labels=c(paste("0", enu_n_0,sep='\n'), paste("1", enu_n_1,sep='\n'), paste("2", enu_n_2,sep='\n')))), xlab = "enu", ylab = "freaks_per")


wilcox.test(Fish[Fish$enu==0,]$freaks_per, Fish[Fish$enu==1,]$freaks_per)


dev.off()
getwd()

