---
title: "Statistics with boxplots"
author: "Aleksandr Kuzmin"
date: "2023-01-11"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width=12, fig.height=8)
```

```{r}
rm(list=ls(all=TRUE))
library(ggplot2)
library(gridExtra)
library(ggpubr)
```

### Upload file with all information
```{r echo=TRUE}
Fish = read.table('../data/fishes_shok.txt', header=TRUE)
```

### Change numbers to factors
```{r echo=TRUE}
Fish$family = as.factor(Fish$family)
Fish$mode = as.factor(Fish$mode)
Fish$mode_scr = as.factor(Fish$mode_scr)
Fish$time = as.factor(Fish$time)
Fish$enu = as.factor(Fish$enu)
```

```{r}
enu_n_0 = paste('N=', nrow(Fish[Fish$enu == 0 & Fish$temperature == 20, ]), sep='')
enu_n_1 = paste('N=', nrow(Fish[Fish$enu == 1 & Fish$temperature == 20, ]), sep='')
enu_n_2 = paste('N=', nrow(Fish[Fish$enu == 2 & Fish$temperature == 20, ]), sep='')

enu_n_0_unclear = paste('N=', nrow(Fish[Fish$enu == 0,]), sep='')
enu_n_1_unclear = paste('N=', nrow(Fish[Fish$enu == 1,]), sep='')
enu_n_2_unclear = paste('N=', nrow(Fish[Fish$enu == 2,]), sep='')
Fish_wth_tm = Fish[Fish$temperature == 20,]
```

# ENU without temperature
```{r}
pdf(file='../figures/ENU_10.01.23.pdf', width=20, height=20)
ggtitle("Fish without temperature")
```

## Fertilization persent without temperature
```{r}
f0 <- ggplot(Fish[Fish$temperature==20,], (aes(enu, fertilization_per)))+
  geom_boxplot(colour = "gray", notch = FALSE)+
  theme_bw()+
  scale_x_discrete(labels=c(paste("0", enu_n_0,sep='\n'), paste("1", enu_n_1,sep='\n'), paste("2", enu_n_2,sep='\n')))
f <- f0 + geom_point(aes(col=family))+ggtitle("Fertilization percent \n vs ENU")+
  xlab("Dose (ENU)") + ylab("Fertilization percent")

```

### Statistics
```{r}
ANOVA_TEST_ENU_VS_fertilization = aov(Fish_wth_tm$fertilization_per ~ Fish_wth_tm$enu)
summary(ANOVA_TEST_ENU_VS_fertilization)
TukeyHSD(ANOVA_TEST_ENU_VS_fertilization, conf.level=.95)
```

## Hatched vs ENU
```{r}
h0 <- ggplot(Fish[Fish$temperature==20,], (aes(enu, hatched_per)))+
  geom_boxplot(colour = "gray", notch = FALSE)+
  theme_bw()+
  scale_x_discrete(labels=c(paste("0", enu_n_0,sep='\n'), paste("1", enu_n_1,sep='\n'), paste("2", enu_n_2,sep='\n')))
h <- h0 + geom_point(aes(col=family))+ggtitle("Hatched percent \n vs ENU") +
  xlab("Dose (ENU)") + ylab("Hatched percent")

```

### Statistics
```{r}
ANOVA_TEST_ENU_VS_hatched = aov(Fish_wth_tm$hatched_per ~ Fish_wth_tm$enu)
summary(ANOVA_TEST_ENU_VS_hatched)
TukeyHSD(ANOVA_TEST_ENU_VS_hatched, conf.level=.95)
```

## Swimming vs ENU
```{r}
s0 <- ggplot(Fish[Fish$temperature == 20, ], (aes(enu, swim_per)))+
  geom_boxplot(colour = "gray", notch = F)+
  theme_bw()+
  scale_x_discrete(labels=c(paste("0", enu_n_0,sep='\n'), paste("1", enu_n_1,sep='\n'), paste("2", enu_n_2,sep='\n')))
s <- s0 + geom_point(aes(col=family))+ggtitle("Swimming percent \n vs ENU")+
  xlab("Dose (ENU)") + ylab("Swimming percent")

```

### Statistics
```{r}
ANOVA_TEST_ENU_VS_swim = aov(Fish_wth_tm$swim_per ~ Fish_wth_tm$enu)
summary(ANOVA_TEST_ENU_VS_swim)
TukeyHSD(ANOVA_TEST_ENU_VS_swim, conf.level=.95)
```

## GGplot with freaks_per
```{r}
fr0 <- ggplot(Fish[Fish$temperature == 20, ], (aes(enu, freaks_per)))+
  geom_boxplot(colour = "gray", notch = F)+
  theme_bw()+
  scale_x_discrete(labels=c(paste("0", enu_n_0,sep='\n'), paste("1", enu_n_1,sep='\n'), paste("2", enu_n_2,sep='\n')))
fr <- fr0 + geom_point(aes(col=family))+ggtitle("Freaks percent \n vs ENU") +
  xlab("Dose (ENU)") + ylab("Freaks percent")

```

### Statistics
```{r}
ANOVA_TEST_ENU_VS_freaks = aov(Fish_wth_tm$freaks_per ~ Fish_wth_tm$enu)
summary(ANOVA_TEST_ENU_VS_freaks)
TukeyHSD(ANOVA_TEST_ENU_VS_freaks, conf.level=.95)
```

```{r}
ggarrange(f, h, s, fr, ncol=2, nrow=2, common.legend=TRUE, legend = 'right')
#dev.off()
```

# Impact of temperature

## Prepare table with ONLY Temperature effect
```{r echo=TRUE}
Fish_temp_intact <- Fish[Fish$enu == 0, ]
```

## Starting PDF
```{r}
pdf('../figures/Temperature__10.01.23.pdf', width=20, height=20)
ggtitle("Fish")
```

### Step sep our exposure time by 0 30 40 50 for the control controls + native
```{r echo=TRUE}
Fish_temp_intact$time = as.factor(Fish_temp_intact$time)
T_0 = paste('N=',nrow(Fish_temp_intact[Fish_temp_intact$time == 0,]),sep='')
T_30 = paste('N=',nrow(Fish_temp_intact[Fish_temp_intact$time == 30,]),sep='')
T_40 = paste('N=',nrow(Fish_temp_intact[Fish_temp_intact$time == 40,]),sep='')
T_50 = paste('N=',nrow(Fish_temp_intact[Fish_temp_intact$time == 50,]),sep='')
```

## Hatched(intact fishes)
```{r}
th0 <- ggplot(Fish_temp_intact, (aes(time, hatched_per)))+
  geom_boxplot(colour = "gray", notch = FALSE)+
  theme_bw()+
  scale_x_discrete(labels=c(paste("0", T_0,sep='\n'), paste("30", T_30,sep='\n'), paste("40", T_40,sep='\n'), paste("50", T_50,sep='\n')))
th <- th0 + geom_point(aes(col=family))+ggtitle("Hatched percent \n Without temperature")+
  xlab("Time NOT exposure") + ylab("Hatched percent")
```

### Statistics
```{r}
ANOVA_TEST_Temp_vs_hatched_per = aov(Fish_temp_intact$hatched_per ~ Fish_temp_intact$time)
summary(ANOVA_TEST_Temp_vs_hatched_per)
```

## Swimming(intact fishes)
```{r}
ts0 <- ggplot(Fish_temp_intact, (aes(time, swim_per)))+
  geom_boxplot(colour = "gray", notch = FALSE)+
  theme_bw()+
  scale_x_discrete(labels=c(paste("0", T_0,sep='\n'), paste("30", T_30,sep='\n'), paste("40", T_40,sep='\n'), paste("50", T_50,sep='\n')))
ts <- ts0 + geom_point(aes(col=family))+ggtitle("Swimming percent \n Without temperature")+
  xlab("Time NOT exposure") + ylab("Swimming percent")

```

### Statistics
```{r}
ANOVA_TEST_Temp_VS_swim_per = aov(Fish_temp_intact$swim_per ~ Fish_temp_intact$time)
summary(ANOVA_TEST_Temp_VS_swim_per)
```

## Freaks(intact fishes)
```{r}
tfr0 <- ggplot(Fish_temp_intact, (aes(time, freaks_per)))+
  geom_boxplot(colour = "gray",notch = FALSE)+
  theme_bw()+
  scale_x_discrete(labels=c(paste("0", T_0,sep='\n'), paste("30", T_30,sep='\n'), paste("40", T_40,sep='\n'), paste("50", T_50,sep='\n')))
tfr <- tfr0 + geom_point(aes(col=family))+ggtitle("Freaks percent \n Without temperature")+
  xlab("Time NOT exposure") + ylab("Freaks percent")

```

### Statistics
```{r}
ANOVA_TEST_Temp_VS_freaks_per = aov(Fish_temp_intact$freaks_per ~ Fish_temp_intact$time)
summary(ANOVA_TEST_Temp_VS_freaks_per)
```

```{r}
ggarrange(th, ts, tfr, ncol=2, nrow=2, common.legend=TRUE, legend = 'right')
dev.off()
```

# ENU + TIME
```{r}
pdf(file='../figures/ENU_Temperature_10.01.23.pdf', width=20, height=20)
```

## ENU VS Fertilization percent
```{r}
ttf01 <- ggplot(Fish, (aes(mode_scr, fertilization_per, fill = enu)))+
  geom_boxplot()+
  theme_bw()
ttf011 <- ttf01+ geom_point(aes(pch=family))+ggtitle("Fertilization percent \n vs ENU")+
  xlab("ENU") + ylab("Fertilization percent")
ttf011 = ttf011 + theme_bw() + theme(axis.text = element_text(size = 6))

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_Fertilization = manova(cbind(temperature, enu) ~ fertilization_per, data = Fish)
summary(MANOVA_TEST_ENU_Temp_VS_Fertilization)
```

## ENU VS Hatched percent + Temperature
```{r}
tth01 <- ggplot(Fish, (aes(mode_scr, hatched_per, fill=enu)))+
  geom_boxplot()+
  theme_bw()
tth011 <- tth01+ geom_point(aes(pch=family))+ggtitle("Hatched percent \n vs ENU + Temperature")+
  xlab("ENU") + ylab("Hatched percent")
tth011 = tth011 + theme_bw() + theme(axis.text = element_text(size = 6))

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_Hatched = manova(cbind(temperature, enu) ~ hatched_per, data = Fish)
summary(MANOVA_TEST_ENU_Temp_VS_Hatched)
```

## TIME + ENU VS Swimming percent
```{r}
tts01 <- ggplot(Fish, (aes(mode_scr, swim_per, fill=enu)))+
  geom_boxplot()+
  theme_bw()
tts011 <- tts01+ geom_point(aes(pch=family))+ggtitle("Swimming percent \n vs ENU + Temperature")+
  xlab("ENU + Temperature") + ylab("Swimming percent")
tts011 = tts011 + theme_bw()+ theme(axis.text = element_text(size = 6))

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_SWimming = manova(cbind(temperature, enu) ~ swim_per, data = Fish)
summary(MANOVA_TEST_ENU_Temp_VS_SWimming)
```

## TIME + ENU VS Freaks percent
```{r}
ttfr01 <- ggplot(Fish, (aes(mode_scr, freaks_per, fill = enu)))+
  geom_boxplot()+
  theme_bw()
ttfr011 <- ttfr01+ geom_point(aes(shape=family))+ggtitle("Freaks percent \n vs ENU + Temperature")+
  xlab("ENU + Temperature") + ylab("Freaks percent")
ttfr011 = ttfr011 + theme_bw()+ theme(axis.text = element_text(size = 6))

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_Freaks = manova(cbind(temperature, enu) ~ freaks_per, data = Fish)
summary(MANOVA_TEST_ENU_Temp_VS_Freaks)
```

```{r}
ggarrange(ttf011, tth011, tts011, ttfr011, ncol=2, nrow=2, common.legend=TRUE, legend = 'right')
dev.off()
```

# ENU + TEMPERATURE IN FAMILIE

### Separate families 
```{r echo=TRUE}
Fish_1x1 = Fish[Fish$family == '1x1',]
Fish_1x2 = Fish[Fish$family == '1x2',]
Fish_2x1 = Fish[Fish$family == '2x1',]
Fish_2x2 = Fish[Fish$family == '2x2',]
```

```{r}
pdf(file='../figures/ENU_Temperature_Fam_10.01.23.pdf', width=20, height=20)
```

## ENU VS Fertilization percent 1x1
```{r}
ttf01_1x1 <- ggplot(Fish_1x1, (aes(mode_scr, fertilization_per)))+
  geom_boxplot(aes(col=enu))+
  theme_bw()
ttf011_1x1 <- ttf01_1x1+ geom_point(aes(col=mode_scr))+ggtitle("Fertilization percent 1x1\n vs ENU")+
  xlab("ENU") + ylab("Fertilization percent")+ theme(axis.text = element_text(size = 6))

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_Fertilization_1x1 = manova(cbind(temperature, enu) ~ fertilization_per, data = Fish_1x1)
summary(MANOVA_TEST_ENU_Temp_VS_Fertilization_1x1)
```

## ENU VS Fertilization percent family 1x2
```{r}
ttf01_1x2 <- ggplot(Fish_1x2, (aes(mode_scr, fertilization_per)))+
  geom_boxplot(aes(col=mode_scr))+
  theme_bw()
ttf011_1x2 <- ttf01_1x2+ geom_point(aes(col=mode_scr))+ggtitle("Fertilization 1x2 percent \n vs ENU")+
  xlab("ENU") + ylab("Fertilization percent")+ theme(axis.text = element_text(size = 6))

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_Fertilization_1x2 = manova(cbind(temperature, enu) ~ fertilization_per, data = Fish_1x2)
summary(MANOVA_TEST_ENU_Temp_VS_Fertilization_1x2)
```

## ENU VS Fertilization percent family 2x1
```{r}
Fish_2x1$enu=as.factor(Fish_2x1$enu)
ttf01_2x1 <- ggplot(Fish_2x1, (aes(mode_scr, fertilization_per, fill=enu)))+
  geom_boxplot(aes(col=enu))+
  theme_bw()
ttf011_2x1 <- ttf01_2x1+ geom_point(aes(col=enu))+ggtitle("Fertilization percent 2x1 \n vs ENU")+
  xlab("ENU") + ylab("Fertilization percent")+ theme(axis.text = element_text(size = 6))
ttf011_2x1 = ttf011_2x1 + theme_bw()

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_Fertilization_2x1 = manova(cbind(temperature, enu) ~ fertilization_per, data = Fish_2x1)
summary(MANOVA_TEST_ENU_Temp_VS_Fertilization_2x1)
```

## ENU VS Fertilization percent family 2x2
```{r}
ttf01_2x2 <- ggplot(Fish_2x2, (aes(mode_scr, fertilization_per)))+
  geom_boxplot(aes(col=mode_scr))+
  theme_bw()
ttf011_2x2 <- ttf01_2x2+ geom_point(aes(col=mode_scr))+ggtitle("Fertilization percent 2x2 \n vs ENU")+
  xlab("ENU") + ylab("Fertilization percent")+ theme(axis.text = element_text(size = 6))

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_Fertilization_2x2 = manova(cbind(temperature, enu) ~ fertilization_per, data = Fish_2x2)
summary(MANOVA_TEST_ENU_Temp_VS_Fertilization_2x2)
```

## Time+ENU VS Hatched percent 1x1
```{r}
tth01_1x1 <- ggplot(Fish_1x1, (aes(mode_scr, hatched_per)))+
  geom_boxplot(aes(col=mode_scr))+
  theme_bw()
tth011_1x1 <- ttf01_1x1+ geom_point(aes(col=mode_scr))+ggtitle("Hatched percent 1x1 \n vs Time+ENU")+
  xlab("Time+ENU") + ylab("Hatched percent")+ theme(axis.text = element_text(size = 6))

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_Hatched_1x1 = manova(cbind(temperature, enu) ~ hatched_per, data = Fish_1x1)
summary(MANOVA_TEST_ENU_Temp_VS_Hatched_1x1)
```

## Time+ENU VS Hatched percent 1x2
```{r}
tth01_1x2 <- ggplot(Fish_1x2, (aes(mode_scr, hatched_per)))+
  geom_boxplot(aes(col=mode_scr))+
  theme_bw()
tth011_1x2 <- ttf01_1x2+ geom_point(aes(col=mode_scr))+ggtitle("Hatched percent 1x2 \n vs Time+ENU")+
  xlab("Time+ENU") + ylab("Hatched percent")+ theme(axis.text = element_text(size = 6))

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_Hatched_1x2 = manova(cbind(temperature, enu) ~ hatched_per, data = Fish_1x2)
summary(MANOVA_TEST_ENU_Temp_VS_Hatched_1x2)
```

## Time+ENU VS Hatched percent 2x1
```{r}
tth01_2x1 <- ggplot(Fish_2x1, (aes(mode_scr, hatched_per)))+
  geom_boxplot(aes(col=mode_scr))+
  theme_bw()
tth011_2x1 <- ttf01_2x1+ geom_point(aes(col=enu))+ggtitle("Hatched percent 2x1 \n vs Time+ENU")+
  xlab("Time+ENU") + ylab("Hatched percent")
tth011_2x1 = tth011_2x1 + theme_bw()+ theme(axis.text = element_text(size = 6))
```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_Hatched_2x1 = manova(cbind(temperature, enu) ~ hatched_per, data = Fish_2x1)
summary(MANOVA_TEST_ENU_Temp_VS_Hatched_2x1)
```

## Time+ENU VS Hatched percent 2x2
```{r}
tth01_2x2 <- ggplot(Fish_2x2, (aes(mode_scr, hatched_per)))+
  geom_boxplot(aes(col=mode_scr))+
  theme_bw()
tth011_2x2 <- ttf01_2x2+ geom_point(aes(col=mode_scr))+ggtitle("Hatched percent 2x2 \n vs Time+ENU")+
  xlab("Time+ENU") + ylab("Hatched percent")+ theme(axis.text = element_text(size = 6))

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_Hatched_2x2 = manova(cbind(temperature, enu) ~ hatched_per, data = Fish_2x2)
summary(MANOVA_TEST_ENU_Temp_VS_Hatched_2x2)
```

```{r}
ggarrange(tth011_1x1, tth011_1x2, tth011_2x1, tth011_2x2, ncol=2, nrow=2, common.legend=TRUE, legend = 'right')
```

## ENU VS Swimming percent 1x1
```{r}
tts01_1x1 <- ggplot(Fish_1x1, (aes(mode_scr, swim_per)))+
  geom_boxplot(aes(col=mode_scr))+
  theme_bw()
tts011_1x1 <- tts01_1x1+ geom_point(aes(col=mode_scr))+ggtitle("Swimming percent 1x1 \n vs Time+ENU")+
  xlab("Time+ENU") + ylab("Swimming percent")+ theme(axis.text = element_text(size = 6))

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_SWimming_1x1 = manova(cbind(temperature, enu) ~ swim_per, data = Fish_1x1)
summary(MANOVA_TEST_ENU_Temp_VS_SWimming_1x1)
```

## ENU VS Swimming percent 1x2
```{r}
tts01_1x2 <- ggplot(Fish_1x2, (aes(mode_scr, swim_per)))+
  geom_boxplot(aes(col=mode_scr))+
  theme_bw()
tts011_1x2 <- tts01_1x2+ geom_point(aes(col=mode_scr))+ggtitle("Swimming percent 1x2 \n vs Time+ENU")+
  xlab("Time+ENU") + ylab("Swimming percent")+ theme(axis.text = element_text(size = 6))

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_SWimming_1x2 = manova(cbind(temperature, enu) ~ swim_per, data = Fish_1x2)
summary(MANOVA_TEST_ENU_Temp_VS_SWimming_1x2)
```

## ENU VS Swimming percent 2x1
```{r}
tts01_2x1 <- ggplot(Fish_2x1, (aes(mode_scr, swim_per)))+
  geom_boxplot(aes(col=mode_scr))+
  theme_bw()
tts011_2x1 <- tts01_2x1+ geom_point(aes(col=mode_scr))+ggtitle("Swimming percent 2x1 \n vs Time+ENU")+
  xlab("Time+ENU") + ylab("Swimming percent")+ theme(axis.text = element_text(size = 6))

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_SWimming_2x1 = manova(cbind(temperature, enu) ~ swim_per, data = Fish_2x1)
summary(MANOVA_TEST_ENU_Temp_VS_SWimming_2x1)
```

## ENU VS Swimming percent 2x2
```{r}
tts01_2x2 <- ggplot(Fish_2x2, (aes(mode_scr, swim_per)))+
  geom_boxplot(aes(col=mode_scr))+
  theme_bw()
tts011_2x2 <- tts01_2x2+ geom_point(aes(col=mode_scr))+ggtitle("Swimming percent 2x2 \n vs Time+ENU")+
  xlab("Time+ENU") + ylab("Swimming percent")+ theme(axis.text = element_text(size = 6))

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_SWimming_2x2 = manova(cbind(temperature, enu) ~ swim_per, data = Fish_2x2)
summary(MANOVA_TEST_ENU_Temp_VS_SWimming_2x2)
```

```{r}
ggarrange(tts011_1x1, tts011_1x2, tts011_2x1, tts011_2x2, ncol=2, nrow=2, common.legend=TRUE, legend = 'right')
```

## ENU VS Freaks percent 1x1
```{r}
ttfr01_1x1 <- ggplot(Fish_1x1, (aes(mode_scr, freaks_per)))+
  geom_boxplot(aes(col=mode_scr))+
  theme_bw()
ttfr011_1x1 <- ttfr01_1x1+ geom_point(aes(col=mode_scr))+ggtitle("Freaks percent 1x1 \n vs Time+ENU")+
  xlab("Time+ENU") + ylab("Freaks percent")+ theme(axis.text = element_text(size = 6))

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_Freaks_1x1 = manova(cbind(temperature, enu) ~ freaks_per, data = Fish_1x1)
summary(MANOVA_TEST_ENU_Temp_VS_Freaks_1x1)
```

## ENU VS Freaks percent 1x2
```{r}
ttfr01_1x2 <- ggplot(Fish_1x2, (aes(mode_scr, freaks_per)))+
  geom_boxplot(aes(col=mode_scr))+
  theme_bw()
ttfr011_1x2 <- ttfr01_1x2+ geom_point(aes(col=mode_scr))+ggtitle("Freaks percent 1x2 \n vs Time+ENU")+
  xlab("Time+ENU") + ylab("Freaks percent")+ theme(axis.text = element_text(size = 6))

```

### Stastics
```{r}
MANOVA_TEST_ENU_Temp_VS_Freaks_1x2 = manova(cbind(temperature, enu) ~ freaks_per, data = Fish_1x2)
summary(MANOVA_TEST_ENU_Temp_VS_Freaks_1x2)
```

## ENU VS Freaks percent 2x1
```{r}
ttfr01_2x1 <- ggplot(Fish_2x1, (aes(mode_scr, freaks_per)))+
  geom_boxplot(aes(col=mode_scr))+
  theme_bw()
ttfr011_2x1 <- ttfr01_2x1+ geom_point(aes(col=mode_scr))+ggtitle("Freaks percent 2x1 \n vs Time+ENU")+
  xlab("Time+ENU") + ylab("Freaks percent")+ theme(axis.text = element_text(size = 6))

```

### Statistics
```{r}
MANOVA_TEST_ENU_Temp_VS_Freaks_2x1 = manova(cbind(temperature, enu) ~ freaks_per, data = Fish_2x1)
summary(MANOVA_TEST_ENU_Temp_VS_Freaks_2x1)
```

## ENU VS Freaks percent 2x2
```{r}
ttfr01_2x2 <- ggplot(Fish_2x2, (aes(mode_scr, freaks_per)))+
  geom_boxplot(aes(col=mode_scr))+
  theme_bw()
ttfr011_2x2 <- ttfr01_2x2+ geom_point(aes(col=mode_scr))+ggtitle("Freaks percent 2x2 \n vs Time+ENU")+
  xlab("Time+ENU") + ylab("Freaks percent")+ theme(axis.text = element_text(size = 6))
```

```{r}
ggarrange(ttfr011_1x1, ttfr011_1x2, ttfr011_2x1, ttfr011_2x2, ncol=2, nrow=2, common.legend=TRUE, legend = 'right')
dev.off()
```
